---
title: "URL Analysis"
author: "K. Bret Staudt Willet"
date: "11/12/2019"
output:
  pdf_document:
    toc: yes
  html_document:
    float_toc: yes
    toc: yes
---

# Get set up

This section loads the data and packages and starts to process the data, but doesn't calculate any statistics or create any results.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
usethis::use_git_ignore(c("*.csv", "*.rds"))
```

## Load packages

```{r, include=FALSE}
library(tidyverse)
library(longurl)
library(urltools)
```

## Load the data

Having completed the steps in the setup.Rmd file, you now have the dataset stored in your local repository and can load it as usual. 

```{r, include=FALSE}
full_tweets_og <- readRDS("downloadedTweets_full.rds")
```

# Review the full dataset

```{r, include=FALSE}
full_tweets <- full_tweets_og %>%
        mutate(full_urls = unlist(urls_url),
               domains = domain(full_urls))
```

Create a vector of domain shorteners.

```{r, include=FALSE}
shorteners <- c("bit.ly", "ow.ly", "buff.ly", "goo.gl", "ln.is", "tinyurl.com", 
                "share.es", "ht.ly", "fb.me", "wp.me", "ift.tt")
```

Create a function to find domains.

```{r, include=FALSE}
find_domain <- function(x) {
    expand_urls(x) %>% 
                pull(expanded_url) %>% 
                domain() %>%
                gsub("www[0-9]?.", "", .)
}
```

Now, an example:

```{r, include=TRUE, echo=TRUE}
find_domain("bit.ly/2SfWO3K")
```

Expand all URLs and pull domain for whole dataset.

```{r, include=TRUE, echo=FALSE}
full_tweets <- full_tweets %>%
        mutate(new_domains = map_if(domains, 
                                    function(x) x %in% shorteners,
                                    find_domain()
                                    )
               )
```

Create a table of results.

```{r, include=TRUE, echo=FALSE}
domains_table <- full_tweets$new_domains %>%
        table() %>%
        as.data.frame() %>%
        sort(desc(Freq))
```

# Version/dependencies

```{r, session-info}
sessionInfo()
```